Linear Stochastic Approximation- Constant Step-Size and Iterate Averaging

### 2017-05-09 instance.tex
rearraged

\section{Instance Dependent Bounds}\label{sec:mainresults}
In this section, we derive instance dependent bounds  which is valid for a fixed $P$ and in the \Cref{sec:uniform}, address the question of deriving uniform bounds $\forall\,P\in \P$, where $\P$ is a class of distributions over $\C^{\dcd}$. We first present the results and then follow it up with a discussion.
\begin{lemma}\label{lm:pd}
Let $P$ be a positive definite distribution over $\C^{\dcd}$, then there exists an $\alpha_P$ such that $\rhod{P}>0$ and $\rhos{P}>0,~\forall \alpha \in (0,\alpha_P)$.
\end{lemma}
\begin{comment}
\begin{proof}
\begin{align*}
\rhos{P}&=\inf_{x:\norm{x}=1}x^* (A_P+A_P^*)x -\alpha x^*\EE{A_t^* A_t} x\\
&=\inf_{x:\norm{x}=1}x^* (A_P+A_P^*)x -\alpha x^* A^*_P A_P -\alpha x^* \EE{M_t^* M_t} x\\
&\geq \lambda_{\min}(A^*_P+A_P)-\alpha \norm{A_P}^2-\sigma^2_P
\end{align*}
The proof is complete by choosing $\alpha_P<\frac{\lambda_{\min}(A^*_P+A_P)}{\norm{A_P}^2+\sigma^2_P}$
\end{proof}
\end{comment}
\begin{lemma}\label{lm:simtran}[Similarity Transformation]
Let $P^{AS}$ be asymptotically stable, then there exists a $U\in \gln$ such that $P^{AS}_U$ is positive definite.
\end{lemma}

@@

\end{theorem}

\begin{theorem}\label{thm:simtran}[Change of Basis]
Let $P$ in \Cref{assmp:lsa}-~\ref{dist} be AS. Define $\gamma_t\eqdef U^{-1}\theta_t,\,,\gamma^*\eqdef U^{-1}\ts$, and suppose if $P_U$ is positive definite, then
\EE{\norm{\gh_t-\gamma^*}^2}
\leq
\left(1+\frac2{\alpha\rhod{P_U}}\right)\frac{\norm{U^{-1}}^2}{\alpha \rhos{P_U}}
\left(\frac{\norm{\theta_0-\ts}^2}{(t+1)^2}+ \frac{\alpha^2(\sigma_P^2\norm{\ts}^2+\sigma_b^2)+\alpha (\sigma_P^2\norm{\ts})\norm{\theta_0-\ts}}{t+1} \right)\,.
%\left(\frac{\norm{\gamma_0-\gamma^*}^2}{(t+1)^2}+ \frac{\alpha^2(\sigma_P^2\norm{\ts}^2+\sigma_b^2)+\alpha (\sigma_P^2\norm{\ts})\norm{\gamma_0-\gamma^*}}{t+1} \right)\,.
%\left(\frac{\norm{\gamma_0-\gamma^*}^2}{(t+1)^2}+ \frac{\alpha^2{\sigma}_1^2+ {\sigma}_2^2 (\alpha^2+\alpha \norm{\gamma_0-\gamma^*})}{t+1} \right)\,,
where $\gh_t=\frac{1}{t+1}\sum_{s=0}^t \gamma_s$.
\end{theorem}
\begin{corollary}\label{cor:as}
Let $P$ in \Cref{lsadist} be asymptotically stable. Then, there exists
\EE{\norm{\thh_t-\ts}^2}
\leq
\left(1+\frac2{\alpha\rhod{P_U}}\right)\frac{\cond{U}^2}{\alpha \rhos{P_U}}
\left(\frac{\norm{\theta_0-\ts}^2}{(t+1)^2}+ \frac{\alpha^2(\sigma_P^2\norm{\ts}^2+\sigma_b^2)+\alpha (\sigma_P^2\norm{\ts})\norm{\theta_0-\ts}}{t+1} \right)\,.
\end{corollary}

@@

\begin{example}\label{ex:pdas}
Matrices $A_1=\begin{bmatrix} 2 &1 \\-1 &0\end{bmatrix}$$A_2=\begin{bmatrix}1 & -1\\ 1 &0 \end{bmatrix}$ and $A_3=\begin{bmatrix} 1 & 10-\epsilon \\ 0 &1 \end{bmatrix}$ are not positive definite. However choosing $U_1=\begin{bmatrix} \frac{1}{\sqrt{2}}& -\frac{1}{\sqrt{2}}\\ -\frac{1}{\sqrt{2}} &\frac{1}{\sqrt{2}} \end{bmatrix}$, $U_2=\begin{bmatrix} \frac{\sqrt{2}}{1-i\sqrt{3}} & \frac{\sqrt{2}}{1+i\sqrt{3}} \\ -\frac{1}{\sqrt{2}} &\frac{1}{\sqrt{2}}\end{bmatrix}$ and $U_3=\begin{bmatrix} 1 & 0\\ 0 &\frac{1}{10} \end{bmatrix}$, we can see that matrices $J_i=U_i^{-1}A_i U_i,i=1,2,3$ are positive definite.

@@

\item \textbf{Geometric Series:} In simple terms the error dynamics is akin to sum of a geometric series with common factor $\alpha\rho$, a fact that is illustrated by the simple $1$-dimensional example in \Cref{ex:geo}.

@@

\item \textbf{Lower Bounds:}
Consider the LSA with $b_t=0$, and $P^0$ has all the mass concentrated on $A_{P^0}=\begin{bmatrix} \lambda_{\min} &0\\ 0& \lambda_{\max}\end{bmatrix}$, for some $\lambda_{\max}>\lambda_{\min}>0$. Note that in this example $\ts=0$.
By choosing $\alpha<\frac2{\lambda_{\max}}$, in this case it is straightforward to write the expression for $\eh_t$ explicitly as below:
\eh_t&=\frac{1}{t+1}\sum_{s=0}^t e_t = \frac{1}{t+1}\sum_{s=0}^t (I-\alpha A_P)^{t-s} e_0\\
&=\frac{1}{t+1}(\alpha A)^{-1}\left(I-(I-\alpha A)^{t+1}\right)e_0
\norm{\eh_t}^2&=\frac{1}{(t+1)^2}\norm{(\alpha A_P)^{-1}\left(I-(I-\alpha A_P)^{t+1}\right)e_0}^2
&\leq\frac{1}{(t+1)^2}\alpha^2\norm{A_P^{-1}}^2\norm{e_0}^2
\norm{\eh_t}^2\geq \eh^2_t(1)=\frac{1}{(t+1)^2}(\alpha \lambda_{\min})^{-2}(1-\alpha \lambda_{\min}^t) \theta^2_0(1)
Note that in this example, $\rhos{P^0}=\rhod{P^0}=\lambda_{\min} -\alpha \lambda_{\min}^2=\lambda_{\min}(1-\alpha \lambda_{\min})$. Sandwiching the error between the lower and upper bounds we have
\frac{1}{(t+1)^2}(\alpha \lambda_{\min})^{-2}(1-\alpha \lambda_{\min}^t) \theta^2_0(1)\leq \norm{\eh_t}^2\leq
\frac{1}{(t+1)^2} \left(\alpha^{-1}\rhos{P^0}+\alpha^{-2}\rhos{P^0}^2\right)\norm{\theta_0}^2

@@

\paragraph{Related Work}

>>>>

\section{Main Results}\label{sec:mainresults}
In this section, we derive instance dependent bounds  which is valid for a fixed $P$ and in the \Cref{sec:uniform}, address the question of deriving uniform bounds $\forall\,P\in \P$, where $\P$ is a class of distributions over $\C^{\dcd}$. We first present the results and then follow it up with a discussion.
\begin{lemma}\label{lm:pd}
Let $P$ be a positive definite distribution over $\C^{\dcd}$, then there exists an $\alpha_P$ such that $\rhod{P}>0$ and $\rhos{P}>0,~\forall \alpha \in (0,\alpha_P)$.
\end{lemma}
\begin{comment}
\begin{proof}
\begin{align*}
\rhos{P}&=\inf_{x:\norm{x}=1}x^* (A_P+A_P^*)x -\alpha x^*\EE{A_t^* A_t} x\\
&=\inf_{x:\norm{x}=1}x^* (A_P+A_P^*)x -\alpha x^* A^*_P A_P -\alpha x^* \EE{M_t^* M_t} x\\
&\geq \lambda_{\min}(A^*_P+A_P)-\alpha \norm{A_P}^2-\sigma^2_P
\end{align*}
The proof is complete by choosing $\alpha_P<\frac{\lambda_{\min}(A^*_P+A_P)}{\norm{A_P}^2+\sigma^2_P}$
\end{proof}
\end{comment}
\begin{lemma}\label{lm:simtran}[Similarity Transformation]
Let $P^{AS}$ be asymptotically stable, then there exists a $U\in \gln$ such that $P^{AS}_U$ is positive definite.
\end{lemma}

@@

\end{theorem}
\begin{theorem}\label{thm:simtran}[Change of Basis]
Let $P$ in \Cref{assmp:lsa}-~\ref{dist} be AS. Define $\gamma_t\eqdef U^{-1}\theta_t,\,,\gamma^*\eqdef U^{-1}\ts$, and suppose if $P_U$ is positive definite, then
\begin{align*}
\EE{\norm{\gh_t-\gamma^*}^2}
\leq
\left(1+\frac2{\alpha\rhod{P_U}}\right)\frac{\norm{U^{-1}}^2}{\alpha \rhos{P_U}}
\left(\frac{\norm{\theta_0-\ts}^2}{(t+1)^2}+ \frac{\alpha^2(\sigma_P^2\norm{\ts}^2+\sigma_b^2)+\alpha (\sigma_P^2\norm{\ts})\norm{\theta_0-\ts}}{t+1} \right)\,.
%\left(\frac{\norm{\gamma_0-\gamma^*}^2}{(t+1)^2}+ \frac{\alpha^2(\sigma_P^2\norm{\ts}^2+\sigma_b^2)+\alpha (\sigma_P^2\norm{\ts})\norm{\gamma_0-\gamma^*}}{t+1} \right)\,.
%\left(\frac{\norm{\gamma_0-\gamma^*}^2}{(t+1)^2}+ \frac{\alpha^2{\sigma}_1^2+ {\sigma}_2^2 (\alpha^2+\alpha \norm{\gamma_0-\gamma^*})}{t+1} \right)\,,
\end{align*}
where $\gh_t=\frac{1}{t+1}\sum_{s=0}^t \gamma_s$.
\end{theorem}
\begin{corollary}\label{cor:as}
Let $P$ in \Cref{lsadist} be asymptotically stable. Then, there exists
\begin{align*}
\EE{\norm{\thh_t-\ts}^2}
\leq
\left(1+\frac2{\alpha\rhod{P_U}}\right)\frac{\cond{U}^2}{\alpha \rhos{P_U}}
\left(\frac{\norm{\theta_0-\ts}^2}{(t+1)^2}+ \frac{\alpha^2(\sigma_P^2\norm{\ts}^2+\sigma_b^2)+\alpha (\sigma_P^2\norm{\ts})\norm{\theta_0-\ts}}{t+1} \right)\,.
\end{align*}
\end{corollary}
\begin{theorem}[Lower Bound]
There exists a $P$ such that
\begin{align}
\frac{1}{(t+1)^2}(\alpha \lambda_{\min})^{-2}(1-\alpha \lambda_{\min}^t) \theta^2_0(1)\leq \norm{\eh_t}^2\leq
\frac{1}{(t+1)^2} \left(\alpha^{-1}\rhos{P^0}+\alpha^{-2}\rhos{P^0}^2\right)\norm{\theta_0}^2
\end{align}

\end{theorem}
\begin{comment}
Consider the LSA with $b_t=0$, and $P^0$ has all the mass concentrated on $A_{P^0}=\begin{bmatrix} \lambda_{\min} &0\\ 0& \lambda_{\max}\end{bmatrix}$, for some $\lambda_{\max}>\lambda_{\min}>0$. Note that in this example $\ts=0$.
By choosing $\alpha<\frac2{\lambda_{\max}}$, in this case it is straightforward to write the expression for $\eh_t$ explicitly as below:
\begin{align*}
\eh_t&=\frac{1}{t+1}\sum_{s=0}^t e_t = \frac{1}{t+1}\sum_{s=0}^t (I-\alpha A_P)^{t-s} e_0\\
&=\frac{1}{t+1}(\alpha A)^{-1}\left(I-(I-\alpha A)^{t+1}\right)e_0
\end{align*}

\begin{align*}
\norm{\eh_t}^2&=\frac{1}{(t+1)^2}\norm{(\alpha A_P)^{-1}\left(I-(I-\alpha A_P)^{t+1}\right)e_0}^2
&\leq\frac{1}{(t+1)^2}\alpha^2\norm{A_P^{-1}}^2\norm{e_0}^2
\end{align*}

\begin{align*}
\norm{\eh_t}^2\geq \eh^2_t(1)=\frac{1}{(t+1)^2}(\alpha \lambda_{\min})^{-2}(1-\alpha \lambda_{\min}^t) \theta^2_0(1)
\end{align*}
Note that in this example, $\rhos{P^0}=\rhod{P^0}=\lambda_{\min} -\alpha \lambda_{\min}^2=\lambda_{\min}(1-\alpha \lambda_{\min})$. Sandwiching the error between the lower and upper bounds we have
\begin{align}
\frac{1}{(t+1)^2}(\alpha \lambda_{\min})^{-2}(1-\alpha \lambda_{\min}^t) \theta^2_0(1)\leq \norm{\eh_t}^2\leq
\frac{1}{(t+1)^2} \left(\alpha^{-1}\rhos{P^0}+\alpha^{-2}\rhos{P^0}^2\right)\norm{\theta_0}^2
\end{align}
\end{comment}

@@

@@

\subsection{Illustrative Examples}
\begin{example}\label{ex:pdas}
Matrices $A_1=\begin{bmatrix} 2 &1 \\-1 &0\end{bmatrix}$$A_2=\begin{bmatrix}1 & -1\\ 1 &0 \end{bmatrix}$ and $A_3=\begin{bmatrix} 1 & 10-\epsilon \\ 0 &1 \end{bmatrix}$ are not positive definite. However choosing $U_1=\begin{bmatrix} \frac{1}{\sqrt{2}}& -\frac{1}{\sqrt{2}}\\ -\frac{1}{\sqrt{2}} &\frac{1}{\sqrt{2}} \end{bmatrix}$, $U_2=\begin{bmatrix} \frac{\sqrt{2}}{1-i\sqrt{3}} & \frac{\sqrt{2}}{1+i\sqrt{3}} \\ -\frac{1}{\sqrt{2}} &\frac{1}{\sqrt{2}}\end{bmatrix}$ and $U_3=\begin{bmatrix} 1 & 0\\ 0 &\frac{1}{10} \end{bmatrix}$, we can see that matrices $J_i=U_i^{-1}A_i U_i,i=1,2,3$ are positive definite.
\end{example}
\paragraph{Remark}

@@

\paragraph{Geometric Series:} In simple terms the error dynamics is akin to sum of a geometric series with common factor $\alpha\rho$, a fact that is illustrated by the simple $1$-dimensional example in \Cref{ex:geo}.

@@

\subsection{Related Work}

### 2017-05-09 intro.tex
rearraged

It is of interest to understand the effect of the step-sizes (a quantity that can be controlled by the algorithm designer) on the performance of the LSA. The choice of the step-sizes $\alpha_t$ needs to trade-off learning rate versus filtering noise, so to speak. In general, one can guess that larger step-sizes might lead to faster learning and at the same time smaller step-sizes are better at handling the noise. A technique in literature that goes back to \cite{polyak,ruppert} is to use a constant step-size (CS) $\alpha_t=\alpha>0,\forall t\geq 0$  in conjunction with averaging of iterates , known as Polyak-Rupert (PR) averaging to filter the noise. The averaged iterates can be given by $\th_t\eqdef\frac{1}{t}\sum_{s=0}^t \theta_t$. Under the CS-PR technique $\theta_t$ is the internal vairable and $\thh_t$ is the output of the algorithm. Intuitively, the CS-PR technique can be seen to address the learning vs filtering trade-off, where the constant step-size takes care of the learning  and the averaging of the iterates takes care of the filtering. \par

@@

 We only assume that $\EE{A_t}$ is Hurwitz, i.e., all its eigenvalues have positive real parts. This is the condition used in prior works by \cite{polyak-judisky,borkarbook}. Eventhough our proof technique resembles that by \cite{bach}, in addition, we make use of Jordon/Cyclic decomposition in a critical way to handle the general Hurwitz assumption. Our results are applicable to wide variety of TD algorithms such as TD(0), GTD/GDT2, TDC. Further, the error dynamics has a simple interpretation in terms of behaviour of the sum of terms in a geometric series, and hence offers a simple and unified understanding of the various TD algroithms.

>>>>

It is of interest to understand the effect of the step-sizes (a quantity that can be controlled by the algorithm designer) on the performance of the LSA. The choice of the step-sizes $\alpha_t$ needs to trade-off learning rate versus filtering noise, so to speak. In general, one can guess that larger step-sizes might lead to faster learning and at the same time smaller step-sizes are better at handling the noise. A technique in literature that goes back to \cite{polyak-judisky,ruppert} is to use a constant step-size (CS) $\alpha_t=\alpha>0,\forall t\geq 0$  in conjunction with averaging of iterates , known as Polyak-Rupert (PR) averaging to filter the noise. The averaged iterates can be given by $\th_t\eqdef\frac{1}{t}\sum_{s=0}^t \theta_t$. Under the CS-PR technique $\theta_t$ is the internal vairable and $\thh_t$ is the output of the algorithm. Intuitively, the CS-PR technique can be seen to address the learning vs filtering trade-off, where the constant step-size takes care of the learning  and the averaging of the iterates takes care of the filtering. \par

@@

 We only assume that $\EE{A_t}$ is Hurwitz, i.e., all its eigenvalues have positive real parts. This assumption is quite common in literatures and appreas in the works by \cite{polyak-judisky,borkarbook}. Eventhough our proof technique resembles that by \cite{bach}, in addition, we make use of Jordon/Cyclic decomposition in a critical way to handle the general Hurwitz assumption. Our results are applicable to wide variety of TD algorithms such as TD(0), GTD/GDT2, TDC. Further, the error dynamics has a simple interpretation in terms of behaviour of the sum of terms in a geometric series, and hence offers a simple and unified understanding of the various TD algroithms.

### 2017-05-09 prob.tex
rearraged

Note that the computation of $\theta_t$ can also be performed in an incremental fashion using $O(d)$ storage. Owning to the special form of $A_t$, sometimes the matrix-vector product $A_t \theta_{t-1}$ can be efficiently computed in $O(d)$ time. This happens for example when $A_t$ is rank one; examples of this kind arising in reinforcemnet learning \cite{} and linear prediction \cite{} will be presented in a later sections (\Cref{sec:rl,sec:lp}). The significance of efficient computation of the matrix-vector product is that then an update of the algorithm

@@

The idea of constant step size and iterate averaging is not new and goes back to \cite{}, where it was first shown that $L_t\ra 0$ as $t\ra\infty$. Recently \cite{bach} revisited the idea in connection to the stochastic gradient descent (SGD) algorithm (which is also an LSA of the form in \eqref{eq:lsa}) to solve linear regression. Much similar to the spirit of \cite{bach}, our aim here is to understand the aspects that effect the behaviour of $L_t$, such as:

>>>>

Note that the computation of $\theta_t$ can also be performed in an incremental fashion using $O(d)$ storage. Owning to the special form of $A_t$, sometimes the matrix-vector product $A_t \theta_{t-1}$ can be efficiently computed in $O(d)$ time. This happens for example when $A_t$ is rank one; examples of this kind arising in reinforcemnet learning \cite{sutton,konda-tsitsiklis,gtd,gtd2,gtdmp} and linear prediction \cite{bach,bachaistats} will be presented in a later sections (\Cref{sec:rl,sec:lp}). The significance of efficient computation of the matrix-vector product is that then an update of the algorithm

@@

The idea of constant step size and iterate averaging is not new and goes back to \cite{polyak-judisky}, where it was first shown that $L_t\ra 0$ as $t\ra\infty$. Recently \cite{bach} revisited the idea in connection to the stochastic gradient descent (SGD) algorithm (which is also an LSA of the form in \eqref{eq:lsa}) to solve linear regression. Much similar to the spirit of \cite{bach}, our aim here is to understand the aspects that effect the behaviour of $L_t$, such as:

### 2017-05-09 related.tex
rearraged

\end{tabular}
}
\label{tb:rates}
\end{table}
\paragraph{Related Work in RL} The various temporal difference learning algorithms can be written as in \Cref{table:td}. The TD(0) algorithm is an on-policy algorithm ($\mu_t=1$) and is unstable in the general {off-policy} setting. The gradient temporal difference (GTD) algorithm \cite{} is stable in off-policy setting as well. Recent work by \cite{korda-prashanth} derive finite time bounds for the TD(0) for two different cases of step-sizes one without PR averaging and other with PR averaging. In the case without PR averaging, \cite{korda-prashanth} consider step-sizes of the form $\frac{c_0c}{c+t}$, where $c_0$ and $c$ are problem dependent positive constants, to dervie a rate of $O(\frac{1}{t})$ for the MSE.  In the case with PR averaging (row $1$ of \Cref{tb:rates}), \cite{korda-prashanth} consider step-size of the from $c_0\left(\frac{c}{c+t}\right)^\delta,\,\delta \in (1/2,1)$ where $c_0, c$ are problem independent positive constants, and show that this choice yeilds a rate of $O(\frac{1}{t})$ for $\delta \ra 1$ and $t\geq t_0$ (where $t_0$ is a problem dependent time instant). A possible limiting feature of the results by \cite{korda-prashanth} is that either the problem knowledge is required or the bounds hold only after a problem dependent time. A centered TD(0) variant is also considered by \cite{korda-prashanth}, however, a projection operator is required to keep the iterates bounded. Also, the bounds by \cite{korda-prashanth} don't have an explicit bias variance decomposition. The works on GTD and TDC by \cite{gtdfirst,tdc} show only asymptotic convergence w.p.1. Recently, the work by \cite{dtdmp} shows a rate of $\frac{1}{\sqrt{t}}$ for GTD with use of projection operation, and also proposed a variant namely GTD-Mirror-prox based on stochastic mirror-prox ideas which achieves $\frac{1}{\sqrt{t}}$ rate without use of projection. In comparison, we don't use of projections, our bounds hold for all time $t$, and the bounds are dependent on the problem instance only to the extent of choosing a step-size that leads to stable behavior, in which case we show that $O\frac{1}{t}$ rate holds (the scaling factor hidden in the $O$ expression is problem dependent). Further, our results provide explicit bias variance decomposition.

>>>>

\end{tabular}
}
\label{tb:rates}
\end{table}
\paragraph{Related Work in RL} The various temporal difference learning algorithms can be written as in \Cref{table:td}. The TD(0) algorithm is an on-policy algorithm ($\mu_t=1$) and is unstable in the general {off-policy} setting. The gradient temporal difference (GTD) algorithm \cite{gtd,gtd2,gtdmp} is stable in off-policy setting as well. Recent work by \cite{korda-prashanth} derive finite time bounds for the TD(0) for two different cases of step-sizes one without PR averaging and other with PR averaging. In the case without PR averaging, \cite{korda-prashanth} consider step-sizes of the form $\frac{c_0c}{c+t}$, where $c_0$ and $c$ are problem dependent positive constants, to dervie a rate of $O(\frac{1}{t})$ for the MSE.  In the case with PR averaging (row $1$ of \Cref{tb:rates}), \cite{korda-prashanth} consider step-size of the from $c_0\left(\frac{c}{c+t}\right)^\delta,\,\delta \in (1/2,1)$ where $c_0, c$ are problem independent positive constants, and show that this choice yeilds a rate of $O(\frac{1}{t})$ for $\delta \ra 1$ and $t\geq t_0$ (where $t_0$ is a problem dependent time instant). A possible limiting feature of the results by \cite{korda-prashanth} is that either the problem knowledge is required or the bounds hold only after a problem dependent time. A centered TD(0) variant is also considered by \cite{korda-prashanth}, however, a projection operator is required to keep the iterates bounded. Also, the bounds by \cite{korda-prashanth} don't have an explicit bias variance decomposition. The works on GTD and TDC by \cite{gtd,gtd2} show only asymptotic convergence w.p.1. Recently, the work by \cite{gtdmp} shows a rate of $\frac{1}{\sqrt{t}}$ for GTD with use of projection operation, and also proposed a variant namely GTD-Mirror-prox based on stochastic mirror-prox ideas which achieves $\frac{1}{\sqrt{t}}$ rate without use of projection. In comparison, we don't use of projections, our bounds hold for all time $t$, and the bounds are dependent on the problem instance only to the extent of choosing a step-size that leads to stable behavior, in which case we show that $O\frac{1}{t}$ rate holds (the scaling factor hidden in the $O$ expression is problem dependent). Further, our results provide explicit bias variance decomposition.
